Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-12 ppdp24/examples.tex
checkpoint

\begin{definition}
  For all $\alpha \in \{ \mesg{w}, \flip{w} \}$ define:
  $$\pmf(\macgv{\alpha} = v) \defeq \sum_{\sigma) \in A} \pmf(\sigma')$$
  and define:
  $$\condd{\pmf}{X}{\macgv{\alpha} = v}(\sigma) \defeq  \sum_{\sigma' \in A} \condd{\pmf}{X}{\sigma'}(\sigma)$$
  where $A = \{ \store \in \mems(\{ \elab{\alpha}{1},\elab{\alpha}{2} \} ) \mid
      \cod{\store(\elab{\alpha}{1}) + \store(\elab{\alpha}{2})} = v \}$.
\end{definition}

>>>>

\begin{definition}
  For all $\alpha \in \{ \mesg{w}, \flip{w} \}$ define:
  $$\pmf(\macgv{\alpha} = v) \defeq \sum_{\sigma \in A} \pmf(\sigma')$$
  and define:
  $$\condd{\pmf}{X}{\macgv{\alpha} = v}(\sigma) \defeq  \sum_{\sigma' \in A} \condd{\pmf}{X}{\sigma'}(\sigma)$$
  where $A = \{ \store \in \mems(\{ \elab{\alpha}{1},\elab{\alpha}{2} \} ) \mid
      \cod{\store(\elab{\alpha}{1}) + \store(\elab{\alpha}{2})} = v \}$.
\end{definition}
